<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  cache = TRUE,
  cache.path = "README-cache/"
)
```

# stackbigquery

<!-- badges: start -->
<!-- badges: end -->

stackbigquery is a package wrapping the Stack Overflow database on Google BigQuery.

This is a minimal example of using [dbcooper](https://github.com/dgrtwo/dbcooper) to create a database package:

* Create a connection in [connections.R](https://github.com/dgrtwo/stackbigquery/blob/master/R/connections.R)
* Run `dbcooper::dbc_init()` on that connection in [zzz.R](https://github.com/dgrtwo/stackbigquery/blob/master/R/zzz.R)
* Put package-specific functions in other files like  [summarize.R](https://github.com/dgrtwo/stackbigquery/blob/master/R/summarize.R)

## Installation

You can install the development version of stackbigquery from GitHub with:

``` r
devtools::install_github("dgrtwo/stackbigquery")
```

You'll also need to create a Google Cloud project with BigQuery enabled, and set two environment variables in your `.Renviron` file (see [bigrquery](https://bigrquery.r-dbi.org/)).

```
BIGQUERY_BILLING_PROJECT=<your_project>
BIGQUERY_EMAIL=<your_email>
```

The first time you use the package, it may prompt you to authenticate (see the [gargle](https://gargle.r-lib.org/) package for more).

## Examples

Once you've loaded the stackbigquery package, you can use functions prefixed with `stack_` to access the database. This includes

* `stack_list()` to list tables in the database
* `stack_query()` to run a SQL query (and get a remote dbplyr table)

```{r posts_questions}
library(dplyr)
library(stackbigquery)

stack_list()
stack_query("SELECT * FROM tags ORDER BY count DESC")
```

You can also use autocomplete-friendly table accessors:

```{r}
stack_posts_questions()
```

These can be used with dbplyr to do joins or summaries.

```{r by_month}
by_month <- stack_posts_questions() %>%
  group_by(month = DATE_TRUNC(DATE(creation_date), MONTH)) %>%
  summarize(n_questions = n(),
            avg_score = mean(score),
            avg_answers = mean(answer_count)) %>%
  collect()

by_month
```

```{r}
library(ggplot2)
theme_set(theme_light())

by_month %>%
  filter(n_questions >= 100) %>%
  ggplot(aes(month, avg_score)) +
  geom_line() +
  labs(y = "Average score of Stack Overflow questions")
```

### Summarize tags

As a database-specific package, stackbigquery also offers useful verbs for doing common operations on the data.

For instance, `summarize_tags` takes a (potentially grouped) version of `stack_posts_questions`, joins it to the tags table, and aggregates the frequency by tag.

```{r by_month_tag}
by_month_tag <- stack_posts_questions() %>%
    group_by(month = DATE_TRUNC(DATE(creation_date), MONTH)) %>%
    summarize_tags(c("javascript", "java", "python", "c#", "php", "c++"))

by_month_tag
```

```{r by_month_tag_plot, dependson = "by_month_tag"}
library(ggplot2)
library(forcats)

by_month_tag %>%
  filter(month != max(month),
         month != min(month)) %>%
  arrange(month) %>%
  mutate(tag = fct_reorder(tag, -percent, last)) %>%
  ggplot(aes(month, percent, color = tag)) +
  geom_line() +
  scale_y_continuous(labels = scales::percent_format()) +
  expand_limits(y = 0) +
  labs(x = "Time",
         y = "% of Stack Overflow questions")
```

### Code of Conduct

Please note that the 'stackbigquery' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
